RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-11 main.tex
:paintbrush: Update table layout

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}

@@

% PGF/TikZ
\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning,shapes}
\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,decorations.shapes,shapes.geometric}
\usepgfplotslibrary{groupplots,patchplots}
\pgfplotsset{compat=newest}
% algpseudocode
\makeatletter
\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
\makeatother
\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
\algrenewcommand{\algorithmicdo}{}

@@

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\begin{tabularx}{\textwidth}{XXXXXXX}
			\toprule
			                              & \gls{mbc}               & \gls{bbc}               & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                       & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                       & 1                       & 2 (competitive)                                 & 2 (collaborative)                            & 1                               & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation  & Backscatter modulation  & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming             & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                     & ---                     & No                                              & Active beamforming                           & ---                             & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                     & ---                     & No                                              & Joint detection or \gls{sic}                 & ---                             & Backscatter detection as primary channel training \\ \midrule
			Backscatter detection         & Coherent or noncoherent & Coherent or noncoherent & Semi-coherent or noncoherent                    & Coherent                                     & ---                             & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable            & Equiprobable            & Equiprobable                                    & Gaussian or Equiprobable                     & Degenerate (\gls{csi}-adaptive) & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow            & Fast or slow            & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow     & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}

@@

% PGF/TikZ
\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning,shapes}
\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,decorations.shapes,shapes.geometric}
\usepgfplotslibrary{groupplots,patchplots}
\pgfplotsset{compat=newest}

% tabularx, ragged2e
\newcolumntype{L}{>{\RaggedRight}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\renewcommand\tabularxcolumn[1]{m{#1}}

% algpseudocode
\makeatletter
\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
\makeatother
\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
\algrenewcommand{\algorithmicdo}{}

@@

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		% \begin{tabularx}{\textwidth}{LLLLLLL}
		% 	\toprule
		% 	                              & \gls{mbc}               & \gls{bbc}               & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                       & RIScatter                                         \\ \midrule
		% 	Coexisting systems            & 1                       & 1                       & 2 (competitive)                                 & 2 (collaborative)                            & 1                               & 2 (collaborative)                                 \\ \midrule
		% 	Scatterer contribution        & Backscatter modulation  & Backscatter modulation  & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming             & Backscatter modulation and passive beamforming    \\ \midrule
		% 	Cooperative transmission      & ---                     & ---                     & No                                              & Active beamforming                           & ---                             & Active beamforming and smart reflection           \\ \midrule
		% 	Cooperative reception         & ---                     & ---                     & No                                              & Joint detection or \gls{sic}                 & ---                             & Backscatter detection as primary channel training \\ \midrule
		% 	Backscatter detection         & Coherent or noncoherent & Coherent or noncoherent & Semi-coherent or noncoherent                    & Coherent                                     & ---                             & Semi-coherent                                     \\ \midrule
		% 	Reflection state distribution & Equiprobable            & Equiprobable            & Equiprobable                                    & Gaussian or Equiprobable                     & Degenerate (\gls{csi}-adaptive) & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
		% 	Load-switching frequency      & Fast or slow            & Fast or slow            & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow     & Fast or slow                                      \\ \bottomrule
		% \end{tabularx}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			                              & \gls{mbc}               & \gls{bbc}               & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                       & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                       & 1                       & 2 (competitive)                                 & 2 (collaborative)                            & 1                               & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation  & Backscatter modulation  & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming             & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                     & ---                     & No                                              & Active beamforming                           & ---                             & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                     & ---                     & No                                              & Joint detection or \gls{sic}                 & ---                             & Backscatter detection as primary channel training \\ \midrule
			Backscatter detection         & Coherent or noncoherent & Coherent or noncoherent & Semi-coherent or noncoherent                    & Coherent                                     & ---                             & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable            & Equiprobable            & Equiprobable                                    & Gaussian or Equiprobable                     & Degenerate (\gls{csi}-adaptive) & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow            & Fast or slow            & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow     & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}
